Trauma treatment delay

### 2023-11-14 manuscriptlongversion.Rmd
text

---
title: "Trauma treatment delay"
author: "Anton Wasielewski"
subtitle: A retrospective cohort study on the factors affecting the delays in trauma
  care
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
editor_options:
  markdown:
    wrap: 72
---

@@

The results show that generally, patients do not systemically receive
delayed treatment because of a patient level factor.

>>>>

---
title: "Trauma treatment delay"
author: "Anton Wasielewski"
subtitle: A retrospective cohort study on the factors affecting the delays in trauma
  care
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
bibliography: bibliography.bib
csl: vancouver.csl
editor_options:
  markdown:
    wrap: 72
---

@@

The results show that generally, patients do not systemically receive
delayed treatment because of a patient level factor. This should be seen
as a good thing, as it suggests that the delayed treatment happens more
at random than because of a factor on a patient level.
